Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming

### 2023-01-10 paper.Rmd
Tue Jan 10 21:00:08 CET 2023: update-remote.sh

```{r full_run_realWorldSymReg_performance, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv", sep=","),
  caption="Performance - Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

>>>>

```{r full_run_realWorldSymReg_performance, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

# Create the data frame from csv
df <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv",
  sep=",",
  colClasses = c("character", "numeric", "character", "numeric", "numeric", "character")
)

# Create a new dataframe with the modified values of the two columns,
df_bold <- df

for(i in 1:nrow(df)){
  if(df[i, "DAE.GP"] < df[i, "Pre.Trained_DAE.GP"]){
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "DAE.GP"],4)))
    df_bold[i, "Pre.Trained_DAE.GP"] <- as.character(round(df[i, "Pre.Trained_DAE.GP"],4))
    }
  else if (df[i, "DAE.GP"] > df[i, "Pre.Trained_DAE.GP"]) {
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "Pre.Trained_DAE.GP"],4)))
  df_bold[i, "DAE.GP"] <- as.character(round(df[i, "DAE.GP"],4))
  }
}
# shorten column names
col_names <- c("Problem", "Hid.Layers", "Set", "DAE-GP", "Pre-Trained", "P-Value")

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c",
 caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=FALSE ) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

### 2023-01-10 slides.Rmd
Tue Jan 10 21:00:08 CET 2023: update-remote.sh

```{r airfoil_fullRun_2hl_maxIndSize_params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_fullRun_2hl_maxIndSize_params"),
  caption="Hyperparameter"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
## Funktions Set

```{r airfoil_function_set, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_function_set"),
  caption="Funktions Set"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

@@

## Zusammenfassung Experimente zur symbolischen Regression

@@

# Create the data frame from csv
df <- read.csv("/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv", sep=",")

@@

for(i in 1:nrow(df)){
  if(df[i, "DAE.GP"] < df[i, "Pre.Trained_DAE.GP"])
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(df_bold[i, "DAE.GP"]))
  else if (df[i, "DAE.GP"] > df[i, "Pre.Trained_DAE.GP"])
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(df_bold[i, "Pre.Trained_DAE.GP"]))
}

# 
knitr::kable(
 df_bold,
 format = "markdown",
 digits = 3,
 caption="Performance - Real World Symbolic Regression Benchmark Problems"
)
%>% row_spec(0,bold=FALSE ) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

## Generalisierungsverhalten

## Lösungsqualität

# Resultate

>>>>

```{r airfoil_fullRun_2hl_maxIndSize_params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_fullRun_2hl_maxIndSize_params"),
  caption="Hyperparameter"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
## Funktions Set Symbolische Regression

```{r airfoil_function_set, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_function_set"),
  #caption="Funktions Set"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

@@

## Mean RMSE - Übersicht

@@

# Create the data frame from csv
df <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv",
  sep=",",
  colClasses = c("character", "numeric", "character", "numeric", "numeric", "character")
)

@@

for(i in 1:nrow(df)){
  if(df[i, "DAE.GP"] < df[i, "Pre.Trained_DAE.GP"]){
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "DAE.GP"],4)))
    df_bold[i, "Pre.Trained_DAE.GP"] <- as.character(round(df[i, "Pre.Trained_DAE.GP"],4))
    }
  else if (df[i, "DAE.GP"] > df[i, "Pre.Trained_DAE.GP"]) {
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "Pre.Trained_DAE.GP"],4)))
  df_bold[i, "DAE.GP"] <- as.character(round(df[i, "DAE.GP"],4))
  }
}
# shorten column names
col_names <- c("Problem", "Hid.Layers", "Set", "DAE-GP", "Pre-Trained", "P-Value")

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c"
 #caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=FALSE ) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

```
## Fitness - Energy Cooling Datensatz

![Energy (Cooling) Datensatz - Fitness über Generationen](~/masterThesis/master_thesis/img/energyCooling_2hl_FullRun_30gens/mean_median_fitness_byGens.png)

## Fitness - Boston Housing Datensatz

![Boston Housing Datensatz - Fitness über Generationen](~/masterThesis/master_thesis/img/bostonHousing_2hl_maxIndSize_fullRun_30gens/mean_median_fitness_byGens.png)

## Auswertung

Keine Evidenz für einen statistisch signifikanten Einfluss von Pre-Training auf die erzielte Lösungsqualität in den durchgeführten Experimenten!
